### 2016-05-19 text/MS.Rmd
changed abstract follwogin Ecology guidelines

1. Metabolic theories posit that body size and temperature are fundamental drivers of ecological patterns and processes, from population to ecosystem levels, because they determine metabolic rates at the individual level. Individual-level metabolic rates tend to scale sub-linearly with body mass and approximately exponentially with temperature, but whether these effects act independently remains a contentious issue.  
2. Most studies of intraspecific scaling of unitary organisms must rely on ontogenetic differences in size to examine its relationship with metabolic rate, thereby potentially confounding age, nutrition or growth rate with size, all of which can affect metabolic rate. In the present study, we use a manipulative approach to test for an association (or lack thereof) between metabolic mass scaling and temperature dependence in four species of colonial marine invertebrates belonging to two phyla. Experimental size manipulation in colonial organisms is of particular relevance to test how ecological processes such as predation and disturbance affect individual physiology and consequently energy flux at population and community levels.  
3. While increased temperature increased metabolic rate in the four species analysed, we found no consistent effect of temperature or growth form on the scaling of metabolic rate with body mass. Two species exhibited independent effects of mass and temperature on metabolic rate, whereas the other two species exhibited decreased and increased mass-scaling exponents with increasing temperature. Importantly, three out of four species consistently presented sub-linear allometric scaling of metabolic rates regardless of experimental temperature. We explore the ecological consequences of how these different metabolic scaling potentially affect energy fluxes at population and community levels.  
4. The allometric scaling of metabolic rate that we observe in the present study contrasts with the isometric scaling of water clearance and feeding rates observed in some colonial marine invertebrates. Our findings suggest that the often observed competitive superiority of colonial over unitary organisms may arise because energy availability for growth and or reproduction (the difference between energy intake and expenditure) increases more strongly with size in colonial organisms.

>>>>

Body size and temperature are fundamental drivers of ecological processes because they determine metabolic rates at the individual level. Whether these drivers act independently on individual-level metabolic rates remains uncertain. Most studies of intraspecific scaling of unitary organisms must rely on pre-existing differences in size to examine its relationship with metabolic rate, thereby potentially confounding size-correlated traits (e.g. age, nutrition) with size, which can affect metabolic rate. Here, we use a size manipulation approach to test whether metabolic mass scaling and temperature dependence interact in four species (two phyla) of colonial marine invertebrates. Size manipulation in colonial organisms allows to test how ecological processes (e.g. predation) affect individual physiology and consequently population- and community-level energy flux. Body mass and temperature interacted in two species, with one species exhibiting decreased and the other increased mass-scaling exponents with increasing temperature. The allometric scaling of metabolic rate that we observe in three species contrasts with the isometric scaling of ingestion rates observed in some colonial marine invertebrates. Thus, we suggest that the often observed competitive superiority of colonial over unitary organisms may arise because the difference between energy intake and expenditure increases more strongly with size in colonial organisms.
